The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-08-27 albatros_paper.tex
HCC fixed one dangler to pretty up the spacing
HCC removed hypen from title for consistency

\title{The Array of Long-Baseline Antennas for Taking Radio
  Observations from the Sub-Antarctic}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.63\linewidth]{Figures/marion_domec_hobart.png}
    \caption{Minimum plasma frequency predicted by the International
      Reference Ionosphere model during the last solar minimum.  At
      some locations on Earth, the plasma frequency may drop as low as
      $\sim1.5$~MHz.}
    \label{Fig:iri}
  \end{center}
\end{figure}

>>>>

\title{The Array of Long Baseline Antennas for Taking Radio
  Observations from the Sub-Antarctic}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.6\linewidth]{Figures/marion_domec_hobart.png}
    \caption{Minimum plasma frequency predicted by the International
      Reference Ionosphere model during the last solar minimum.  At
      some locations on Earth, the plasma frequency may drop as low as
      $\sim1.5$~MHz.}
    \label{Fig:iri}
  \end{center}
\end{figure}
